
---
title: "Merge recipients DIVAT_clean Nantes"
author: "alice"
date: "2024-04-16"
output: html_document
---

## Creation of the table gathering recipient's data at graft time 

```{r}
suppressWarnings(library(Hmisc))
suppressWarnings(library(readxl))

coltype <- c("text","guess","text","guess")
individual <- read_excel("C:\\Alice\\1-Universitée\\Stages\\M1-centrale\\DATAS\\NewDATA\\KiTGENIE_CLEAN2.xlsx", sheet = "individual",na = "NA",col_types = coltype)
coltypes <- c("text","text","text","text","guess","guess","text","text","guess","guess","guess","guess","guess","text","guess","text","guess","guess","guess","guess","guess","guess","guess","guess","guess","guess","guess","text","text","text","text","text","text","text","text","text","text","text","text","text","text","text","text","text","text","text","text","text","text")
graft_base <- read_excel("C:\\Alice\\1-Universitée\\Stages\\M1-centrale\\DATAS\\NewDATA\\KiTGENIE_CLEAN2.xlsx", sheet = "graft_base",na = "NA",col_types = coltypes)
```



merge recipient's individual and grafts

```{r}
individual_r <- individual[individual$type_ind == "R",]
merge1 <- merge.data.frame(individual_r,graft_base,by.x = "id_ind", by.y = "id_r",all.y = TRUE)
merge2 <- unique(merge1)
```




add the antecedents of the recipient

```{r}
suppressWarnings(antecedent_r <- read_excel("C:\\Alice\\1-Universitée\\Stages\\M1-centrale\\DATAS\\NewDATA\\KiTGENIE_CLEAN2.xlsx", sheet = "antecedent_r",na = "NA",col_types = "numeric"))
#antecedent_r_Nantes <- antecedent_r[complete.cases(antecedent_r$id_g),]


merge3 <- merge.data.frame(merge2,antecedent_r, by.x = "id_g",by.y = "id_g",all.x = TRUE)
merge4 <- unique(merge3)
```

add the other grafts of the recipient
```{r}
coltype <- c("text","text","guess","guess","guess","text")
other_grafts <- read_excel("C:\\Alice\\1-Universitée\\Stages\\M1-centrale\\DATAS\\ALICE_DATAS\\ALL_VARIABLES_KiTGENIE2024.xlsx", sheet = "other_grafts",na = "NA",col_types = coltype)
```

```{r}
merge5 <- merge.data.frame(merge4,other_grafts, by.x = "id_ind",by.y = "id_ind_r",all.x=TRUE)
merge6 <- unique(merge5)
```


remove to empty columns (type_ind, center, num_info_other_r, death_r, date_death_r, precision_disease)

```{r}
merge6_clean <- merge6[,-c(3,6,7,10)]
```
 

score for missing datas ()
```{r}
merge6_clean$Nb_NA <- rowSums(is.na(merge6_clean[,1:27]))#)+ 4*(is.na(merge6_clean$abo_ind))+ 4*(is.na(merge6_clean$height_r))+ 4* (is.na(merge6_clean$weight_r))
```

test
```{r}
merge6_clean[merge6_clean$Nb_NA> 15,]
```


remove the recipient with to much missing datas (3 individuals 1 graft each)
```{r}
merge6_clean <- merge6_clean[merge6_clean$Nb_NA < 16,]
```


Create a new worksheet and save this merge into it.
```{r}
OUT <- createWorkbook()
addWorksheet(OUT,"recipient_before")
writeData(OUT,"recipient_before",merge6_clean,keepNA = TRUE)
openxlsx::saveWorkbook(OUT,"C:\\Alice\\1-Universitée\\Stages\\M1-centrale\\DATAS\\NewDATA\\MERGING_part_1.xlsx")
```


## Work on the datas

```{r}
library(corrplot)
library(gplots)
library(FactoMineR)
library(factoextra)
```


gather only numerical datas
```{r}
merge6_clean_n <- data.frame(sapply(merge6_clean[,-c(1,2,4,7,65,66,67)],as.numeric))
```


```{r}
merge6_clean_nor <- scale(merge6_clean_n)
```

```{r}
merge6_clean_n$num_og[is.na(merge6_clean_n$num_og)]<-0
```


```{r fig.height=5, fig.width=12}
correlation_matrix <- cor(merge6_clean_nor[,-c(56,57,59)],use = "pairwise.complete.obs")
corrplot(correlation_matrix,method = "color", type = "upper")
heatmap.2(correlation_matrix,
          Rowv = FALSE, Colv = FALSE,
          dendrogram = "none",
          col = colorRampPalette(c("blue", "white", "red"))(100),
          scale = "none",
          margins = c(10,10))
```

## PCA over the merge

```{r}
pca_r<- PCA(merge6_clean_nor[,c(1,4:59)])
```

```{r}
pca_r_brut <- PCA(merge6_clean_n[,c(1:59)])
```
```{r}
fviz_pca_var(pca_r_brut, col.var = "contrib", gradient.cols = c("white", "#0b53c1", "#ff0055"),ggtheme = theme_minimal())
```

```{r}
fviz_pca_ind(pca_r_brut, label="none", habillage=32, addEllipses=TRUE, ellipse.level=95, palette = c("skyblue4","goldenrod","pink","green","red"))+
theme(plot.title = element_text(face = "bold", size = 12, hjust=0.5),plot.subtitle = element_text(size = 9, hjust=0.5)) + 
  labs(title = "Individuals projection of PCA with 59 quantitative variables", subtitle = "ACP without na.omit = ??? ")
```
58 : num other graft
```{r}
fviz_pca_ind(pca_r_brut, label="none", habillage=58, addEllipses=TRUE, ellipse.level=95, palette = c("skyblue4","goldenrod","pink","green","red"))+
theme(plot.title = element_text(face = "bold", size = 12, hjust=0.5),plot.subtitle = element_text(size = 9, hjust=0.5)) + 
  labs(title = "Individuals projection of PCA with 59 quantitative variables", subtitle = "ACP without na.omit = ??? ")
```

dates
```{r message=FALSE, warning=FALSE}

fviz_pca_ind(pca_r_brut, label="none", habillage=3, addEllipses=TRUE, ellipse.level=95, palette = c("skyblue4","skyblue4","skyblue4","skyblue4","skyblue4","skyblue4","skyblue4","skyblue4","skyblue4","skyblue4","goldenrod","goldenrod","goldenrod","goldenrod","goldenrod","goldenrod","goldenrod","goldenrod","goldenrod","goldenrod","red","red","red","red","red","red","red","red","red","red","green","green","green","green","green","green","green","green","green","green","pink","pink","pink","pink","pink","pink","pink","pink","pink","pink"))+
theme(plot.title = element_text(face = "bold", size = 12, hjust=0.5),plot.subtitle = element_text(size = 9, hjust=0.5)) + 
  labs(title = "Individuals projection of PCA with 59 quantitative variables", subtitle = "ACP without na.omit = ??? ")
```


```{r}
fviz_eig(pca_r_brut, barfill= 'aquamarine4',barcolor = 'aquamarine4',geom="bar",width=0.8,addlabels=T)+ 
  theme(plot.title = element_text(face = "bold", size = 12, hjust=0.5),plot.subtitle = element_text(size = 9, hjust=0.5)) +
  labs(title = "TITLE", subtitle = "Subtitle")
```


```{r}
fviz_contrib(pca_r_brut, "var", axes = 1)
fviz_contrib(pca_r_brut, "var", axes = 2)
fviz_contrib(pca_r_brut, "var", axes = 3)
```


## WPCA over the merge test


determine row weights
```{r}
merge6_clean_w <- merge6_clean
merge6_clean_w$nb_row <- ave(rep(1, nrow(merge6_clean_w)), merge6_clean_w$id_g, FUN = length)

merge6_clean_w_n <- data.frame(sapply(merge6_clean_w[,-c(1,2,4,7,65,66,67)],as.numeric))
```


apply the weight in the PCA 
```{r}
PCA(merge6_clean_w_n[,c(1:59)],row.w = 1/merge6_clean_w_n$nb_row)
```
```{r}
res.impute <- imputeFAMD(merge6_clean)
```

```{r}
res.afdm <- FAMD(merge6_,tab.disj=res.impute$tab.disj) 
```

