---
title: "Exploration DIVAT other_grafts"
author: "alice"
date: "2024-04-16"
output: html_document
---

```{r}
suppressWarnings(library(Hmisc))
suppressWarnings(library(readxl))
suppressWarnings(library(corrplot))
suppressWarnings(library(gplots))
suppressWarnings(library(xlsx))
coltype <- c("text",rep("numeric",94))
suppressWarnings(complications_graft <- read_excel("C:\\Alice\\1-Universitée\\Stages\\M1-centrale\\DATAS\\ALICE_DATAS\\ALL_VARIABLES_KiTGENIE2024.xlsx", sheet = "complications_graft",na = "NA",col_types = coltype))
```

keep datas only from Nantes

```{r}
compli_N_test <- as.numeric(complications_graft$id_g)
compliG_N <- complications_graft[complications_graft$id_g == compli_N_test,]
compliG_N <- compliG_N[complete.cases(compliG_N$id_g),]
```
replace the missing delay (as no event) by -2
```{r}
compliG_N_A <- compliG_N[,-c(1,81,84,85,87,89,90,92,93,94,95)]
for (col in names(compliG_N_A)) {
  compliG_N[[col]][is.na(compliG_N_A[[col]])] <- -2
}
```

Remove recurrence_fsgs (not an off datas) 
```{r}
compliG_N <- compliG_N[,-95]
```


```{r}
describe(compliG_N)
```

missing (NA) : - delay_compli_rhumato : 2721  = nb(compli_rhumato == 0) -> replace by -2
               - delay_compli_pulmo : 3141 ""
               - delay_compli_card : 2430 ""
               - delay_compli_coronaro : 3035 ""
               - delay_compli_InsufCard : 2997 ""
               - delay_compli_vasc...13 : 2619 ""
               - delay_compli_cardVasc : 20261 ""
               - delay_compli_hta :2450 ""
               - delay_compli_arterio : 3020""
               - delay_compli_avc : 3091""
               - delay_compli_lymphoedeme : 3229""
               - delay_compli_mvte : 2939""
               - delay_compli_vasc...29 : 2891""
               - ""

               - transplantectomy_d : 3008 -> replace by 0 ?
               - delay_transplantectomy_d : 3073 -> replace by -2 ?
               - recurence_fsgs : 3185 -> replace by 0 ? random ?

```{r}
dataframe <- data.frame(row.names = c("missing","part","coments") )
lenght <- length(compliG_N$id_g)
for (col in names(compliG_N)) {
  if(sum(is.na(compliG_N[[col]]))!= 0){
    #cat(col ,":" , sum(is.na(biobsy_N[[col]])),"\n")
    dataframe[col] <- c(sum(is.na(compliG_N[[col]])),sum(is.na(compliG_N[[col]]))/lenght,"random")}
}
```  

```{r}
write.xlsx(dataframe, file = "C:\\Alice\\1-Universitée\\Stages\\M1-centrale\\DATAS\\Describe\\explore\\explore_NA.xlsx",sheetName = "complications_graft2", append = TRUE)
```
              
```{r}
compliG_N <- data.frame(sapply(compliG_N,as.character))
```

```{r}
addWorksheet(OUT, "complications_graft")
writeData(OUT, sheet = "complications_graft", x = compliG_N,keepNA = TRUE)
```
    
```{r}
write.xlsx(compliG_N, file = "C:\\Alice\\1-Universitée\\Stages\\M1-centrale\\DATAS\\NewDATA\\ALL_VARIABLES_KITGENIE_CLEAN.xlsx",sheetName = "complications_graft", append = TRUE)
```


```{r}
summary(complications_graft)
```


```{r}
correlation_matrix <- cor(compliG_N_A[,c(2*(0:40)+1)])
corrplot(correlation_matrix,method = "color", type = "upper")
heatmap.2(correlation_matrix,
          Rowv = FALSE, Colv = FALSE,
          dendrogram = "none",
          col = colorRampPalette(c("blue", "white", "red"))(100),
          scale = "none",
          margins = c(10,10))

correlation_matrix <- cor(compliG_N_A[,c(2*(1:41))])
corrplot(correlation_matrix,method = "color", type = "upper")
heatmap.2(correlation_matrix,
          Rowv = FALSE, Colv = FALSE,
          dendrogram = "none",
          col = colorRampPalette(c("blue", "white", "red"))(100),
          scale = "none",
          margins = c(10,10))
```

