---
title: "Exploration DIVAT consult"
author: "alice"
date: "2024-04-16"
output: html_document
---

```{r}
suppressWarnings(library(Hmisc))
suppressWarnings(library(readxl))
suppressWarnings(library(corrplot))
suppressWarnings(library(gplots))
coltype <- c("text",rep("text",32))
consult <- read_excel("C:\\Alice\\1-Universitée\\Stages\\M1-centrale\\DATAS\\ALICE_DATAS\\ALL_VARIABLES_KiTGENIE2024.xlsx", sheet = "consult",na = "NA",col_types = coltype)
```

```{r}
consult_N_test <- as.numeric(consult$id_g)
consult_N <- consult[consult$id_g == consult_N_test,]
consult_N <- consult_N[complete.cases(consult_N$id_g),]
```
```{r}
for (col in names(consult_N)) {
  if(sum(is.na(consult_N[[col]]))!= 0){
    cat(col ,":" , sum(is.na(consult_N[[col]])),"\n")}
}
```


Missing (NA) : - day_consult : 703/32350
               - weight_consult : 2556 -> may be already enter in the base (check id_g equals)
               - height_consult : 179 ""
               - bmi_consult : 2696"" -> can be compute if h & w known
               - creat_consult : 257 -> random ?
               - mdrd_consult : 257   -> random ?
               - ckdepi_consult : 257 -> random ?
               - prot_consult : 6629 -> not calculated ? replace by random?
               - hemoglobin_consult : 3855 ""
               - ttt_hta_consult : 3417 ""
               - cni_consult : 221 -> replace by "Non"?
               - cni_dose_consult : 3965 -> "Non" + random? replace by -2?
               - cni_tx_consult : 20163 -> only prescribe ? replace by -2?
               - antiprolif_consult : 469 -> random ?
               - mmf_consult : 262 -> random ?
               - mmf_dose_consult : (mmf_consult == 0)+ random, replace by "Non"?
               - mpa_consult : 1271 -> random?
               - mpa_dose_consult : 24527 -> ==0 + random -> -2
               - aza_consult : 180 -> random ?
               - aza_dose_consult : 30591 -> ==0 + random -> -2
               - mTor_consult : 1220 -> random ?
               - rapa_consult : 182 -> random ?
               - rapa_dose_consult : 31061 -> ==0 + random -> -2
               - rapa_tx_consult : 31976 -> only highest ? replace by -2?
               - evero_consult : 1224 -> random ?
               - evero_dose_consult : 30445 -> ==0 + random -> -2
               - evero_tx_consult : 31042 -> only part of it ?
               - cs_consult : 334 -> random ?
               - cs_dose_consult : 22236 -> ==0 + random -> -2
               
               
               


```{r}
describe(consult_N)
```


```{r}
summary(consult)
```

