---
title: "Exploration DIVAT consult"
author: "alice"
date: "2024-04-16"
output: html_document
---

```{r}
suppressWarnings(library(Hmisc))
suppressWarnings(library(readxl))
suppressWarnings(library(corrplot))
suppressWarnings(library(gplots))
coltype <- c("text","numeric","numeric",rep("text",30))
consult <- read_excel("C:\\Alice\\1-Universitée\\Stages\\M1-centrale\\DATAS\\ALICE_DATAS\\ALL_VARIABLES_KiTGENIE2024.xlsx", sheet = "consult",na = "NA",col_types = coltype)
```

```{r}
consult_N_test <- as.numeric(consult$id_g)
consult_N <- consult[consult$id_g == consult_N_test,]
consult_N <- consult_N[complete.cases(consult_N$id_g),]
```
Replace the NA from witch we can deduce the value (ask for weight)
```{r}
consult_N$day_consult[is.na(consult_N$day_consult)] <- round(consult_N$month_consult[is.na(consult_N$day_consult)]*30.4167,digits = 0)
consult_N$cni_consult[is.na(consult_N$cni_consult)] <- "Non"
consult_N$cni_dose_consult[is.na(consult_N$cni_dose_consult)] <- 0
consult_N$antiprolif_consult[is.na(consult_N$antiprolif_consult)] <- 0
consult_N$mmf_consult[is.na(consult_N$mmf_consult)] <- 0
consult_N$mmf_dose_consult[is.na(consult_N$mmf_dose_consult)] <- 0
consult_N$mpa_consult[is.na(consult_N$mpa_consult)] <- 0
consult_N$mpa_dose_consult[is.na(consult_N$mpa_dose_consult)] <- 0
consult_N$aza_consult[is.na(consult_N$aza_consult)] <- 0
consult_N$aza_dose_consult[is.na(consult_N$aza_dose_consult)] <- 0
consult_N$mTor_consult[is.na(consult_N$mTor_consult)] <- 0
consult_N$rapa_consult[is.na(consult_N$rapa_consult)] <- 0
consult_N$rapa_dose_consult[is.na(consult_N$rapa_dose_consult)] <- 0
consult_N$evero_dose_consult[is.na(consult_N$evero_dose_consult)] <- 0
consult_N$evero_consult[is.na(consult_N$evero_consult)] <- 0
consult_N$cs_consult[is.na(consult_N$cs_consult)] <- 0
consult_N$cs_dose_consult[is.na(consult_N$cs_dose_consult)] <- 0
```

attempts to solve the weight problem (replace by the mean of weight) and add the number of consult by id_g (failed)
```{r}
nombre_consultations <- table(consult_N$id_g)
consult_N_improved <- consult_N
consult_N_improved$nb_consults <- nombre_consultations[consult_N_improved$id_g]


consult_N_improved$weight_consult <- sapply(consult_N_improved$weight_consult,as.numeric)

avrg_weight_r <- round(tapply(X = consult_N_improved$weight_consult[is.na(consult_N_improved$weight_consult)==FALSE], INDEX = consult_N_improved$id_g[is.na(consult_N_improved$weight_consult)==FALSE], FUN = mean, na.rm = TRUE),2)
for (i in unique(consult_N_improved$id_g)) {
  consult_N_improved$weight_consult[consult_N_improved$id_g == i] <- ifelse(is.na(consult_N_improved$weight_consult[consult_N_improved$id_g == i]), avrg_weight_r[i], consult_N_improved$weight_consult[consult_N_improved$id_g == i])
}
```
Put the size when we already have it
```{r}
consult_N_improved <- consult_N
cons_w_noNA <- consult_N_improved[!is.na(consult_N_improved$height_consult),c(1,7)]
cons_w_noNA<-unique(cons_w_noNA)

for (i in unique(cons_w_noNA$id_g)) {
  consult_N_improved$height_consult[consult_N_improved$id_g == i & is.na(consult_N_improved$height_consult)] <- cons_w_noNA$height_consult[cons_w_noNA$id_g == i]
}

```


```{r}
consult_N_improved <- consult_N_improved[,-c(17,28,31)]

dataframe <- data.frame(row.names = c("missing","part","coments") )
lenght <- length(consult_N$id_g)
sum <- 0
for (col in names(consult_N)) {
  if(sum(is.na(consult_N[[col]]))!= 0){
    sum <- sum + sum(is.na(consult_N_improved[[col]]))
    cat(col ,":" , sum(is.na(consult_N_improved[[col]]))/lenght," : ",sum(is.na(consult_N_improved[[col]])),"\n")
    #missing <- c(missing, sum(is.na(consult_N_improved[[col]]))/lenght)}
    #dataframe[col] <- c(sum(is.na(consult_N[[col]])),sum(is.na(consult_N[[col]]))/lenght,"random")}
}}
print(sum)
```



Missing (NA) : - day_consult : 703/32350
               - weight_consult : 2556 -> may be already enter in the base (check id_g equals)
               - height_consult : 179 ""
               - bmi_consult : 2696"" -> can be compute if h & w known
               - creat_consult : 257 -> random ?
               - mdrd_consult : 257   -> random ?
               - ckdepi_consult : 257 -> random ?
               - prot_consult : 6629 -> not calculated ? replace by random?
               - hemoglobin_consult : 3855 ""
               - ttt_hta_consult : 3417 ""
               - cni_consult : 221 -> replace by "Non"?
               - cni_dose_consult : 3965 -> "Non" + random? replace by -2?
               - cni_tx_consult : 20163 -> only prescribe ? replace by -2?
               - antiprolif_consult : 469 -> random ?
               - mmf_consult : 262 -> random ?
               - mmf_dose_consult : (mmf_consult == 0)+ random, replace by "Non"?
               - mpa_consult : 1271 -> random?
               - mpa_dose_consult : 24527 -> ==0 + random -> -2
               - aza_consult : 180 -> random ?
               - aza_dose_consult : 30591 -> ==0 + random -> -2
               - mTor_consult : 1220 -> random ?
               - rapa_consult : 182 -> random ?
               - rapa_dose_consult : 31061 -> ==0 + random -> -2
               - rapa_tx_consult : 31976 -> only highest ? replace by -2?
               - evero_consult : 1224 -> random ?
               - evero_dose_consult : 30445 -> ==0 + random -> -2
               - evero_tx_consult : 31042 -> only part of it ?
               - cs_consult : 334 -> random ?
               - cs_dose_consult : 22236 -> ==0 + random -> -2
               
               
Save the data frame with the NA indormations               
```{r}
write.xlsx(dataframe, file = "C:\\Alice\\1-Universitée\\Stages\\M1-centrale\\DATAS\\Describe\\explore\\explore_NA.xlsx",sheetName = "consult2", append = TRUE)
```

Less heavy method to save the new table constructed with the consults of Nantes
```{r}
addWorksheet(OUT, "consult_r_modif")
writeData(OUT, sheet = "consult_r_modif", x = consult_N_improved,keepNA = TRUE)
```

```{r}
describe(consult_N)
```


```{r}
summary(consult)
```

