---
title: "Exploration DIVAT donor"
author: "alice"
date: "2024-04-16"
output: html_document
---

```{r}
library(Hmisc)
library(readxl)
suppressWarnings(library(corrplot))
suppressWarnings(library(gplots))
coltype <- c(rep("text",2),"guess",rep("text",4),rep("numeric",3),rep("text",11),rep("numeric",6),"numeric",rep("text",2))
suppressWarnings(donor <- read_excel("C:\\Alice\\1-Universitée\\Stages\\M1-centrale\\DATAS\\ALICE_DATAS\\ALL_VARIABLES_KiTGENIE2024.xlsx", sheet = "donor",na = "NA",col_types = coltype))
```

```{r}
donor_N_test <- as.numeric(donor$id_g)
donor_N <- donor[donor$id_g == donor_N_test,]
donor_N <- donor_N[complete.cases(donor_N$id_g),]
```


```{r}
describe(donor)
```

```{r}
dataframe <- data.frame(row.names = c("missing","part","coments") )
lenght <- length(donor_N$id_ind_d)
for (col in names(donor_N)) {
  if(sum(is.na(donor_N[[col]]))!= 0){
    #cat(col ,":" , sum(is.na(donor_N[[col]])),"\n")}
    dataframe[col] <- c(sum(is.na(donor_N[[col]])),sum(is.na(donor_N[[col]]))/lenght,"random")}
}
```

```{r}
write.xlsx(dataframe, file = "C:\\Alice\\1-Universitée\\Stages\\M1-centrale\\DATAS\\Describe\\explore\\explore_NA.xlsx",sheetName = "donor", append = TRUE)
```
Missing (NA) :

age_predon_d : 7 -> random ?
type_cadaver_d : 3 -> random ?
ecd_scd_d : 412 -> random ?
height_predon_d : 231 -> random correlated with w and bmi ?
weight_predon_d : 231 -> """
bmi_predon_d : 231 -> """
cmv_predon_d : 35 -> random ?
ebv_predon_d : 83 -> random ?
hvc_predon_d : 32 -> random ?
ag_hbs_predon_d : 25 -> random ?
ac_hbs_predon_d : 728 -> random ?
hiv_predon_d : 30 -> random ?
hta_predon_d : 184 -> random ?
diab_predon_d : 639 -> random ?
dyslip_predon_d : 1045 -> random ?
atcdt_arretCardia_predon_d : 63 -> random ?
diuresis_predon_d : 645 -> random ?
urea_predon_d : 467 -> random ?
creat_predon_d : 48 -> random ?
ckdepi_predon_d : 64 -> random ?
clearanceIso_predon_d : 2884 -> too much missing remove ?
prot_predon_d : 407 -> random ?
microAlb_predon_d : 96 -> random ?
hematuria_predon_d : 726 -> random ?
drug_vaso_predon_d : 654 -> random ?

```{r}
summary(donor)
```





