
---
title: "Exploration DIVAT graft_base"
author: "alice"
date: "2024-04-16"
output: html_document
---

```{r}
suppressWarnings(library(Hmisc))
suppressWarnings(library(readxl))
suppressWarnings(library(corrplot))
suppressWarnings(library(gplots))
coltypes <- c("text","text","text","text","guess","guess","text","text","guess","guess","guess","guess","guess","text","guess","text","guess","guess","guess","guess","guess","guess","guess","guess","guess","guess","guess","text","text","text","text","text","text","text","text","text","text","text","text","text","text","text","text","text","text","text","text","text","text")
graft_base <- read_excel("C:\\Alice\\1-Universitée\\Stages\\M1-centrale\\DATAS\\ALICE_DATAS\\ALL_VARIABLES_KiTGENIE2024.xlsx", sheet = "graft_base",na = "NA",col_types = coltypes)
```

```{r}
graft_b_N_test <- as.numeric(graft_base$id_g)
graft_b_N <- graft_base[graft_base$id_g == graft_b_N_test,]
graft_b_N <- graft_b_N[complete.cases(graft_b_N$id_g),]
```

```{r}
describe(graft_b_N)
```

```{r}
for (col in names(graft_b_N)) {
  if(sum(is.na(graft_b_N[[col]]))!= 0){
    cat(col ,":" , sum(is.na(graft_b_N[[col]])),"\n")}
}
```
Missing (NA) :

rank_g : 1 -> random
height_r : 19 -> random
weight_r : 20 -> random
bmi_r : 23 -> random
code_disease : 22 -> random
precision_disease : 3247 -> remove column as no data at all
delay_abm_g : 100 -> random
delay_dial_g : 648 -> no dial ?
mach_perf : 745 -> random
nb_dial_post_g : 161 -> random
day_resemption_fct_g : 106 -> random
cold_ischemia_g : 27 -> random
luk_ischemia_g : 2035 -> random
day_hospit_g : 1032 -> random ?
cmv_r : 31 -> random
ebv_r : 113 -> random
hcv_r : 34 -> random
ag_hbs_r : 29 -> random
ac_hbs_r : 75 -> random
hiv_r : 44 -> random
transfusion_r : 186 -> random
day_ttt_ind : 1508 -> ???
prophyl_pnc_g : 41 -> random
prophyl_cmv_g : 36 -> random


```{r}
summary(graft_base)
```



