---
title: "Exploration DIVAT living_donor"
author: "alice"
date: "2024-04-16"
output: html_document
---

```{r}
suppressWarnings(library(Hmisc))
suppressWarnings(library(readxl))
living_donor <- read_excel("C:\\Alice\\1-Universitée\\Stages\\M1-centrale\\DATAS\\ALICE_DATAS\\ALL_VARIABLES_KiTGENIE2024.xlsx", sheet = "living_donor",na = "NA")

```

```{r}
ld_N <- living_donor[living_donor$center == "Nantes",]
```


```{r}
describe(ld_N)
```

```{r}
dataframe <- data.frame(row.names = c("missing","part","coments") )
lenght <- length(ld_N$id_ind_ld)
for (col in names(ld_N)) {
  if(sum(is.na(ld_N[[col]]))!= 0){
    #cat(col ,":" , sum(is.na(ld_N[[col]])),"\n")}
    dataframe[col] <- c(sum(is.na(ld_N[[col]])),sum(is.na(ld_N[[col]]))/lenght,"random")}
}
```

```{r}
write.xlsx(dataframe, file = "C:\\Alice\\1-Universitée\\Stages\\M1-centrale\\DATAS\\Describe\\explore\\explore_NA.xlsx",sheetName = "living_donor", append = TRUE)
```
Missing (NA) : 

               - relation_rld : 36 -> replace by "no relationship" ?
               - age_predon_d : 3 -> random
               - weightKg_don_ld : 6 -> random
               - heightCm_don_ld : 6 -> random
               - bmi_don_ld : 6 -> -> random
               - corp_surface_don_ld : 6 -> random
               - abo_ld : 7 -> random
               - birthWeightG_ld : 240 -> random
               - htn_don_ld : 6 -> random
               - holter_don_ld : 37 -> random or "Normal"
               - diabetes_don_ld : 6 -> random
               - dyslipidemia_don_ld : 7 -> random
               - hdlGL_don_ld : 113 -> random
               - ldlGL_don_ld : 73 -> random
               - chstlGL_don_ld : 35 -> random
               - triglycGL_don_ld : 22 -> random
               - hepato_don_ld : 6 -> random
               - smoker_ld : 7 -> random
               - creat¬µmolL_don_ld : 6 -> random
               - ckdepi_don_ld : 6 -> random
               - protU_don_ld : 47 -> random
               - microAlb_don_ld : 65 -> random ???
               - clearCock_don_ld : 45 -> random
               - clearIso_don_ld : 29 -> random
               - c1cr_don_ld : 101 -> random ???
               - hematU_don_ld : 12 -> random
               - ecbu_don_ld : 12 -> random
               - coag_don_ld : 14 -> random
               - psa_don_ld : 329 -> non calculated -> remove column or change to no value ???
               - radioPoumon_don_ld : 30 -> random
               - scanAr_don_ld : 21 -> random
               - nbArt_don_ld : 258 -> non notted -> remove column or change to no value ???
               - nbVeine_don_ld : 382 -> non notted -> remove column or change to no value ???
               - echoAbdo_don_ld : 22 -> random
               - echoRenal_don_ld : 14 -> random
               - echoR_anorm_don_ld : 348 -> no echo -> replace by "N" ?
               - echoCard_don_ld : 103 -> random ???
               - gyneco_don_ld : 169 -> random ???
               - ecg_don_ld : 14 -> random
               - crp_don_ld : 23 -> random
               - eprot_don_ld : 12 -> random
               - hiv_don_ld : 16 -> random
               - agP24_don_ld : 120 -> random ???
               - htlv_don_ld : 24 -> random
               - hcv_don_ld : 20 -> random
               - agHBs_don_ld : 12 -> random
               - acHBc_don_ld : 14 -> random
               - acHBs_don_ld : 75 -> random
               - vdrl_don_ld : 27-> random
               - tpha_don_ld : 27 -> random
               - toxo_don_ld : 22 -> random
               - cmv_don_ld : 19 -> random
               - ebv_don_ld : 19 -> random
               - bhisto_don_ld : 22 -> random
               - bder_don_ld : 256 -> random ???
               - tothisto_don_ld : 24 -> random
               - totder_don_ld : 257 -> ????????????????????????????????????????????????????????
               - histo_don_ld : 23 -> random
               - tder_don_ld : 256 -> ??????????????????????????????????????????????????????????
               - techniqueOp_ld : 5 -> random
               - nephrect_ld : 6 -> random
               - sondejj_ld : 290 -> only "Non", missing = "Oui" ?             
               - dureeHospD_ld : 20 -> random
               - nb_visits : 7 -> random
               - max_day_ld : 7 -> random
               - max_month_ld : 7 -> random
               - max_year_ld : 7 -> random
               - nb_visits_minus1year : 16 -> random
               - max_CKDEPI_ld : 7 -> random
               - min_CKDEPI_ld : 7 -> random
               - mean_CKDEPI_ld : 7 -> random
               - max_rcr_ld : 8 -> random
               - min_rcr_ld : 8 -> random
               - mean_rcr_ld : 8 -> random
               - coefpente_CKDEPI_postdon : 14 -> random 
               - r2_pente_CKDEPI_postdon : 14 -> random
               - adj_r2_coefpente_CKDEPI_postdon : 25 -> random
               - max_protU_ld : 100 -> no protU test ? -> random
               - min_protU_ld : 100 -> no protU test ? -> random
               - mean_protU_ld : 100 -> no protU test ? -> random
               - max_MicroAlb_ld : 100 -> no MicroAlb test ? -> random
               - min_MicroAlb_ld : 100 -> no MicroAlb test ? -> random
               - mean_MicroAlb_ld : 100 -> no MicroAlb test ? -> random               
               - max_HDL_ld : 92 -> no HDL test ? -> random
               - min_HDL_ld : 92 -> no HDL test ? -> random
               - mean_HDL_ld : 92 -> no HDL test ? -> random
               - max_LDL_ld : 93 -> no LDL test ? -> random
               - min_LDL_ld : 93 -> no LDL test ? -> random
               - mean_LDL_ld : 93 -> no LDL test ? -> random

```{r}
summary(living_donor)
```

